Towards Transparency and Open Science

### 2023-02-20 manuscript.Rmd
let articles begin on right page
ammend license note

This work (version ``r repro::current_hash(backend = "gert")``) is made available online under the following source under the terms of the [Creative Commons Universal Public Domain Dedication | CC0](https://creativecommons.org/publicdomain/zero/1.0/):
<https://doi.org/10.5281/zenodo.7654989>

@@

\clearpage\newpage

@@

\newpage

@@

>>>>

This work (version ``r repro::current_hash(backend = "gert")``) is made available online under the following source under the terms of the [Creative Commons Universal Public Domain Dedication | CC0](https://creativecommons.org/publicdomain/zero/1.0/), unless noted otherwise:
<https://doi.org/10.5281/zenodo.7654989>

@@

\pagenumbering{gobble}
\cleardoublepage\newpage

@@

\cleardoublepage
\newpage

@@

\cleardoublepage
